---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

#Introduction

R is a statistical program that allows statiscians to conduct analysis on a variation of topics. This ranges from healthcare, academia, finance, and marketing. Pretty much, if there's data for it, R can analyze it. 

This tutorial is a preliminary introduction into running statistical analysis in R.

## Basic Syntax
* Arithemitcs
* Declaring and Initializing Variables


We'll eventually get into the hard statistics and data visualization aspect of R. For now, think of the program as a calculator do simple arithmetics. R has six different sign operators for these arithmetics. 

* `+` Addition - Finding the sum of a set of numbers 

```{r Arithmetic Add, exercise=TRUE}
1 + 1 
```

* `-` Subtraction - Finding the difference of a set of numbers

```{r Arithmetic Subtract, exercise=TRUE}
4 - 2 
```

* `*` Multiplication - Finding the product of a set of numbers

```{r Arithmetic Multiply, exercise=TRUE}
6 * 5 
```

* `/` Division - Finding the quotient of a set of numbers

```{r Arithmetic Divide, exercise=TRUE}
100 / 10
```

* `^` Exponents - Exponent value for a set of numbers 

```{r Arithmetic Exponent, exercise=TRUE}
10^2
```


* `%%` Modulous - Remainder between a set of numbers 

```{r Arithmetic Modulous, exercise=TRUE}
4 %% 2
```

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Now try it yourself! 

What is the sum of 3 and 4?

```{r SumPractice, exercise=TRUE, exercise.eval=TRUE}

```

What is the difference of 10 and 4?

```{r DifferencePractice, exercise=TRUE, exercise.eval=TRUE}

```

What is the product of 3 and 6?

```{r ProductPractice, exercise=TRUE, exercise.eval=TRUE}

```

What is the quotient of 100 and 4?

```{r QuotientPractice, exercise=TRUE, exercise.eval=TRUE}

```

What is the 30 to the power of 3?

```{r ExponentPractice, exercise=TRUE, exercise.eval=TRUE}

```

What is the remainder of 100 divided by 4? 

```{r ModoulousPractice, exercise=TRUE, exercise.eval=TRUE}

```


Quiz Time!!

Answer these questions to help you review the concepts you learned

```{r ArithmeticQuiz}
quiz(
  question("Which sign operator do I use to find the remainder of two values?",
    answer("%%", correct = TRUE),
    answer("/"),
    answer("*"),
    answer("+")
  ),
  question("Which sign operator do I use to find the quotient between two values?",
    answer("%%"),
    answer("/", correct = TRUE),
    answer("*"),
    answer("+")
  )
)
```





### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

